\Title

### 2021-02-16 manuscript/content.tex
Improve gradient-boosting schematic figure
Follow the design discussed on last meeting.
Update the caption of the figure.
Use triangle markers for observation points on every schematic figure.

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that fall inside
    the respective window.
    Since the windows overlap, the total number of sources
    from all sets will be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

>>>>

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (Fig.~\ref{fig:gradient-boosting-schematics}b).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosting algorithm.
        Given a set of data points (blue upwards triangles), define a set of
        equivalent sources (orange dots).
        Start the gradient-boosting algorithm by selecting the data points and
        the sources that fall under one of the overlapping windows, and
        estimate their coefficients by fitting against this portion of the
        data.
        Then predict the effect of this set of sources on every observation
        point and calculate the residuals.
        Use another window to select residual points and sources that fall
        under it, and estimate their coefficients by fitting them against the
        selected residual points.
        Predict the effect of this set of sources on every observation point
        and update the residue.
        Repeat this step for every remaining window.
        The order in which the windows are covered is randomized to improve
        convergence of the algorithm.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}
